A Monte Carlo Synthetic Acceleration Method for Solving the Thermal Radiation Diffusion Equation

### 2012-05-26 doc/jcomp2012/jcomp2012.tex
Added nse07 figures to tex

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{tmadd,tmath}
\usepackage[mathcal]{euscript}

@@

\begin{figure}[htpb!]
  \centerline{
    \input{3D_mesh_segment.pstex_t}}
  \caption{3D mesh-segment.  The particle's current cell (in blue) is
    connected to 6 adjacent cells.  The cell numbers are plotted
    alongside the mesh such that the blue cell has index 7, the high
    $z$ cell has index 2, etc.}
  \label{fig:mesh_segment}
\end{figure}

@@

\begin{figure}[htpb!]
  \centerline{
    \includegraphics[width=5in,clip]{marshak_10.eps}}
  \caption{
    Solution of the Marshak wave problem at $t=10$~sh.  The analytic
    solution is compared to the MCSA solution.  Note that the MCSA,
    PCG, and PFIXED methods all give numerically identical answers.}
  \label{fig:marshak_10}
\end{figure}

@@

\begin{figure}[htpb!]
  \centerline{
    \includegraphics[width=5in,clip]{spectral_radius.eps}}
  \caption{Spectral radius of the iteration matrix, $\ve{H}$, for the
    Marshak Wave problem as a function of elapsed problem time.}
  \label{fig:marshak_spectral}
\end{figure}

@@

\begin{figure}[htpb!]
  \centerline{
    \includegraphics[width=5in,clip]{mrshk_np_CPU.eps}}
  \caption{CPU time versus number of particles per stage for the
    Marshak problem.  The number of particles is the requested number.
    In each stage the exact number can vary depending upon the number
    of cells and source strength per cell.}
  \label{fig:CPU_Np}
\end{figure}

\begin{figure}[htpb!]
  \centerline{
    \includegraphics[width=5in,clip]{mrshk_np_Ns.eps}}
  \caption{
    Maximum number of stages per cycle versus number of particles per
    stage for the Marshak problem.  The number of particles is the
    requested number.  In each stage the exact number can vary
    depending upon the number of cells and source strength per cell.}
  \label{fig:CPU_Ns}
\end{figure}

@@

\begin{figure}[htpb!]
  \centerline{
    \includegraphics[width=5in,clip]{mrshk_wc_CPU.eps}}
  \caption{
    CPU time versus relative weight cutoff for the Marshak problem.
    Results are shown for 10 and 50 requested particles per stage.
    The numbers in parenthesis show the maximum number of particles
    run in a stage during the course of the problem.}
  \label{fig:CPU_wc}
\end{figure}

@@

\begin{table}[htpb!]
  \begin{center}
    \begin{tabular}{lrr}\hline\hline
      \multicolumn{1}{c}{Method} & 
      \multicolumn{1}{c}{Max Iterations} & 
      \multicolumn{1}{c}{Relative CPU Time}\\\hline\hline
      %%
      PCG & 11 & 1.11 \\
      %%
      PFIX & 11 & 1.42 \\
      %%
      MCSA & 11 & 1.0 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{Comparison of solution methods for the Marshak problem. All
    methods were run with a stopping criterion of $\sn{1}{-8}$.  The
    MCSA method used $N_p=10$ and $W_c = \sn{1}{-4}$.  The CPU time is
    measured relative to the MCSA method, which required 72.6 s on a
    3.6~GHz Xeon.}
  \label{tab:marshak_comparision}
\end{table}

@@

\begin{figure}[htpb!]
  \centerline{
    \includegraphics[width=5in,clip]{mesh.eps}}
  \caption{Multi-material problem mesh.  The duct region is blue.  The
    wall is red.  The foil is green.  The mesh is $60\times 60\times
    60$.}
  \label{fig:multi-mat-mesh}
\end{figure}

\begin{figure}[htpb!]
  \centerline{
    \includegraphics[width=5in,clip]{T_multi_mat.eps}}
  \caption{
    Two-dimensional plot of the temperature at 100~sh on a cut-plane
    positioned at the mid-point of the $z$-axis.  The positions of the
    edit points where the time-evolution of the temperature is plotted
    in Fig.~\ref{fig:edit-points} are indicated by the black disks.}
  \label{fig:multi-mat_T}
\end{figure}

\begin{figure}[htpb!]
  \begin{center}
    \begin{tabular}{m{2in}m{4in}}
      \subfigure[Edit points]{\includegraphics[width=2in,clip]{points.eps}} &
      \subfigure[Temperature]{\includegraphics[width=4in,clip]{multi_mat.eps}}
    \end{tabular}
  \end{center}
  \caption{(a) Edit points and (b) time-evolution of the temperature
    at each point.  All points are centered in the $z$-axis.}
  \label{fig:edit-points}
\end{figure}

@@

\begin{table}[htpb!]
  \begin{center}
    \begin{tabular}{lrr}\hline\hline
      \multicolumn{1}{c}{Method} & 
      \multicolumn{1}{c}{Max Iterations} & 
      \multicolumn{1}{c}{Relative CPU Time}\\\hline\hline
      %%
      PCG & 18 & 1.03 \\
      %%
      PFIX & 38 & 1.43 \\
      %%
      MCSA & 20 & 1.0 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{
    Comparison of solution methods for the multi-material problem. All
    methods were run with a stopping criterion of $\sn{1}{-8}$.  The
    MCSA method used $N_p=1000$ and $W_c = \sn{1}{-3}$.  The problem
    was run to an elapsed time of 10~sh.  The MCSA method required 3.4
    hours on a 3.6~GHz Xeon.}
  \label{tab:multimat_comparision}
\end{table}
